Coherent optical association of atoms into a single molecule

### 2020-11-10 paper.tex
Add country to Purdue...
Association ...

\begin{document}
\title{Coherent optical association of a single molecule}
\author{Yichao~Yu}
\email{yichaoyu@g.harvard.edu}
\gradstudent
\author{Kenneth~Wang}
\gradstudent
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906}
\author{Lewis~R.~B.~Picard}
\gradstudent
\author{Jessie~T.~Zhang}
\gradstudent
\author{William~B.~Cairncross}
\harvardccb
\harvardphysics
\cua
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\harvardphysics
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\harvardccb
\harvardphysics
\cua

@@

\begin{abstract}
  Fully controlled single molecules provide a promising platform
  for a variety of quantum science applications.
  As a step towards this goal, we report on coherent association
  of a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  and are created with higher than $60~\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on narrow excited-state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

>>>>

\begin{document}
\title{Coherent optical association of atoms into a single molecule}
\author{Yichao~Yu}
\email{yichaoyu@g.harvard.edu}
\gradstudent
\author{Kenneth~Wang}
\gradstudent
\author{Jonathan~D.~Hood}
\affiliation{Department of Chemistry, Purdue University, West Lafayette, Indianna, 47906, USA}
\author{Lewis~R.~B.~Picard}
\gradstudent
\author{Jessie~T.~Zhang}
\gradstudent
\author{William~B.~Cairncross}
\harvardccb
\harvardphysics
\cua
\author{Jeremy~M.~Hutson}
\affiliation{Joint Quantum Centre Durham-Newcastle, Department of Chemistry, Durham University, Durham, DH1 3LE, United Kingdom}
\author{Till Rosenband}
\harvardphysics
\author{Kang-Kuen~Ni}
\email{ni@chemistry.harvard.edu}
\harvardccb
\harvardphysics
\cua

@@

\begin{abstract}
  Fully controlled single molecules provide a promising platform
  for a variety of quantum science applications.
  As a step towards this goal, we report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  and are created with higher than $60~\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on narrow excited-state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}
